---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kraken

<!-- badges: start -->
[![R-CMD-check](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/aquaMetrics/kraken/branch/main/graph/badge.svg)](https://app.codecov.io/gh/aquaMetrics/kraken?branch=main)
<!-- badges: end -->

The goal of `kraken` [R](https://www.r-project.org/) package is to calculate a
predicted impact area from Fauna IQI, DNA predicted IQI or emamectin benzoate
sampling results. 
 
This package is in an experimental phase. The core algorithm  for calculating
the area is unlikely to change, but the function names as well as the data
formats and structures may change.

## Installation

You can install the most up to date version of `kraken` like so:

```r
install.packages("devtools")
devtools::install_github("aquaMetrics/kraken")
```

Run this code regularly to keep up to date with the latest version. 

## Calculate Area

```{r example}
library(kraken)
```

Illustrative demo data shows how to calculate impact zone area and all relevant
outputs.

```r
output <- kraken(demo_iqi)
head(output)
```

```{r kraken, echo=FALSE, message=FALSE, warning=FALSE}
output <- kraken(demo_iqi, loess = TRUE, n_try = 10)
head(output)
```

The returned dataframe provides responses to `r output$question |> unique() |>  length()`
key questions required to assess the mixing zone. These responses included
station, transect and survey-level outputs. The overall estimated mixing zone
(with 95% confidence) is provided, see `area_95_confidence`.

```r
# area_95 provides the output 
output$response[output$question == "area_95_confidence"]
#> [1] "96914.9237670089"
```

Additionally, numerous other outputs are provided see `?kraken` documentation
for details. For example, check if any warnings returned.

```{r outputs}
output$response[output$question == "area_warning"]
output$response[output$question == "ellipse_warnings"]
```

The `output` dataframe includes a map of the stations and the predicted impact
area and breach points. This is provided in the `object` variable of the
dataframe.

```{r map}
output$object[output$question == "map"]
```

An ellipse is used to approximate the impacted area by spanning the breach
points predicted for each sampling transect such that all given points lie just
inside or on the boundary of the ellipsoid.

# Residue area

To calculate emamectin benzoate sampling results

```r
output <- kraken(demo_residue, method="residue", pass_fail = 763)
head(output)
```

```{r kraken-residue, echo=FALSE, message=FALSE, warning=FALSE}
output <- kraken(demo_residue, n_try = 100, pass_fail = 763, method="residue")
head(output)
```

# Plots

Currently, a function to generate plots for each sampling transect is
undocumented but can be accessed for demonstration purposes. The `method`
parameter must be set to "iqi" or "residue" and the `pass_fail` to match either
IQI standard of "0.64" or the required residue standard.

```{r plots,  message=FALSE, warning=FALSE}
plots <- kraken:::create_plot(output, method = "residue", pass_fail = 763)
```

For example, mocked data for the first transect will look similar to this:

```{r plot, echo=FALSE, message=FALSE, warning=FALSE}
plots[[1]]

```
The plot above shows a dashed green line as standard pass/fail boundary, the
black dashed line shows the predicted breach point. Black points represent each
replicate sample at each sampling station. The hexagon heatmap show the number
of predictions in that area.

# Save Ellipse Shapefile

You save can indicative mixing zone 'ellipse' as a shapefile.

```r 
ellipse <- output$object[output$question == "ellipse"][[1]]
sf::write_sf(ellipse, "ellipse.shp")
```

Other lower-level functions are provided to run specific parts of the validation
and calculation process.

## Help

View documentation for each function in the usual way.

```r
?kraken
?consecutive_stations   
# ...
```

A [issues](https://github.com/aquaMetrics/kraken/issues) to github to discuss
bugs or features.


