---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aquaman

<!-- badges: start -->
[![R-CMD-check](https://github.com/aquaMetrics/aquaman/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aquaMetrics/aquaman/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/aquaMetrics/aquaman/branch/main/graph/badge.svg)](https://app.codecov.io/gh/aquaMetrics/aquaman?branch=main)
<!-- badges: end -->

The goal of `aquaman` R package is to calculate ecology metrics and assess the mixing zone
area, fulfilling these specific steps:

 - Assess the mixing zone area from IQI sampling results (DNA or taxonomic).
 
Possible future development:

 - Assign bacteria taxa from DNA reads using `dada2` package.
 - Model IQI metric from assigned bacteria families.
 
This package is in an experimental phase. The core algorithm  for calculating the
area is unlikely to change, but the functions, and input and output data
structures may change.

## Installation

You can install the development version of `aquaman` like so:

```r
install.packages("devtools")
devtools::install_github("aquaMetrics/aquaman")
```

## Calculate Area

This example shows you how to calculate mixing zone from demo IQI input data:

```{r example}
library(aquaman)
```

```r
## Run the demo IQI data and return the area of the mixing zone
area <- assess(demo_iqi)
area
#> $`5%`
#> [1] 96914.92
#>
#> $`package version`
#> [1] ‘0.2.0’
#> 
#> $`package date`
#> [1] "2022-07-27"
```

Alternatively, it is possible to to see outputs from each step in the process.
As well as add manual overrides for distance to good status or bearing for each
transect:
```r
data <- consecutive_stations(demo_iqi)
probs <- probability_non_linear(data$survey_data)
overrides <- override(probs,
                      overrideTransect1 = 100, # transect1 overrides
                      overrideBearing1 = -47)
breachs <- breach(overrides)
areas <- area(breachs)
```

