---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kraken

<!-- badges: start -->
[![R-CMD-check](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/aquaMetrics/kraken/branch/main/graph/badge.svg)](https://app.codecov.io/gh/aquaMetrics/kraken?branch=main)
<!-- badges: end -->

The goal of `kraken` [R](https://www.r-project.org/) package is to calculate the
mixing zone from Fauna IQI or DNA predicted IQI sampling results.
 
This package is in an experimental phase. The core algorithm  for calculating
the area is unlikely to change, but the function names as well as the data
formats and structures may change.

## Installation

You can install the development version of `kraken` like so:

```r
install.packages("devtools")
devtools::install_github("aquaMetrics/kraken")
```

## Calculate Area

```{r example}
library(kraken)
```

Example shows how to calculate mixing zone and all relevant outputs.

```r
output <- kraken(demo_iqi)
head(output)
```


```{r kraken, echo=FALSE, message=FALSE, warning=FALSE}
output <- kraken(demo_iqi, loess = TRUE, n_try = 10)
head(output)
```

The `output` dataframe provides responses to 30 key questions required to assess
the mixing zone. These responses included station, transect and survey-level
outputs. The overall estimated mixing zone (with 95% confidence) is
provided, see `area_95_confidence`.

```r
# area_95 provides the output 
output$response[output$question == "area_95_confidence"]
#> [1] "96914.9237670089"
```

Additionally, numerous other outputs are provided see `?kraken` documentation
for details. For example, check if any warnings returned.

```{r outputs}
output$response[output$question == "area_warning"]
output$response[output$question == "ellipse_warnings"]
```

The `output` dataframe includes a map of the stations and the indicative
mixing zone. This is provided in the `object` variable of the dataframe.

```{r map}
output$object[output$question == "map"]
```

You save can indicative mixing zone 'ellipse' as a shapefile.

```r 
ellipse <- output$object[output$question == "ellipse"][[1]]
sf::write_sf(ellipse, "ellipse.shp")
```

Other lower-level functions are provided to run specific parts of the validation
and calculation process.

## Help

View documentation for each function in the usual way.

```r
?kraken
?consecutive_stations   
# ...
```

A [issues](https://github.com/aquaMetrics/kraken/issues) to github to discuss
bugs or features.


