---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kraken

<!-- badges: start -->
[![R-CMD-check](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/aquaMetrics/kraken/branch/main/graph/badge.svg)](https://app.codecov.io/gh/aquaMetrics/kraken?branch=main)
<!-- badges: end -->

The goal of `kraken` [R](https://www.r-project.org/) package is to calculate the
mixing zone area from Fauna IQI or DNA predicted IQI sampling results.
 
This package is in an experimental phase. The core algorithm  for calculating
the area is unlikely to change, but the function names as well as the data
formats and structures may change.

## Installation

You can install the development version of `kraken` like so:

```r
install.packages("devtools")
devtools::install_github("aquaMetrics/kraken")
```

## Calculate Area

```{r example}
library(kraken)
```

Example shows how to calculate mixing zone and all relevant outputs.

```r
output <- kraken(demo_iqi)
head(output)
```


```{r kraken, echo=FALSE, message=FALSE, warning=FALSE}
output <- kraken(demo_iqi, loess = TRUE, niter = 10)
head(output)
```


The outputs dataframe includes the overall predicted mixing zone area (ellipse) with 95% confidence as well as related warnings if applicable.

```r
# area_95 provides the output 
output$response[output$question == "area_95_confidence"]
#> [1] "96914.9237670089"
```

```{r outputs}
output$response[output$question == "area_warning"]
output$response[output$question == "ellipse_warnings"]
```

The outputs also include a map of the stations and the indicative ellipse area:

```{r map}
output$object[output$question == "map"]

```

Save indicative ellipse area as shapefile:

```r 
ellipse <- output$object[output$question == "ellipse"][[1]]
sf::write_sf(ellipse[[1]],"ellipse.shp")
```

Other lower-level functions are provided to run specific parts of the validation
and calculation process.

## Help

View documentation for each function in the usual way.

```r
?kraken
?consecutive_stations
# ...
```
