---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kraken

<!-- badges: start -->
[![R-CMD-check](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aquaMetrics/kraken/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/aquaMetrics/kraken/branch/main/graph/badge.svg)](https://app.codecov.io/gh/aquaMetrics/kraken?branch=main)
<!-- badges: end -->

The goal of `kraken` [R](https://www.r-project.org/) package is to calculate the
mixing zone area from IQI sampling results (DNA or taxonomic).
 
This package is in an experimental phase. The core algorithm  for calculating
the area is unlikely to change, but the function names as well as the data
formats and structures may change.

## Installation

You can install the development version of `kraken` like so:

```r
install.packages("devtools")
devtools::install_github("aquaMetrics/kraken")
```

## Calculate Area

This example shows you how to calculate mixing zone from demo IQI input data:

```{r example}
library(kraken)
```

```r
## Run the demo IQI data and return the area of the mixing zone
area <- assess(demo_iqi)
area
#> $`5%`
#> [1] 96914.92
#>
#> $`package version`
#> [1] ‘0.2.0’
#> 
#> $`package date`
#> [1] "2022-07-27"
```

Alternatively, it is possible to to see outputs from each step in the process.
As well as add manual overrides for distance to good status or bearing for each
transect:
```r
data <- consecutive_stations(demo_iqi)
probs <- probability_non_linear(data$survey_data)
overrides <- override(probs,
                      overrideTransect1 = 100, # transect1 overrides
                      overrideBearing1 = -47)
breachs <- breach(overrides)
areas <- area(breachs)
```

## Help

View documentation for each function in the usual way.

```r
?assess
?consecutive_stations
# ...
```


