---
title: "Residue Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Residue Example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning =  FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## Data

Export data from fishfarm database as .csv file. Save locally and use the 'Import Dataset' tool in the Environmment pane to import data or use `read.csv()` funtion and paste in file path - but replace  '\' with '/' in the path.

```{r data}
library(kraken)
library(tidyverse)

test_data <- read.csv("inst/extdat/test-data/residue-test-data.csv")
# Filter data for my particular farm/date of interest
test_data <- filter(test_data, Site.ID == "BELL1")

# Select only the columns needed for calculations
test_data <- select(test_data,
  "Survey_date" = Survey.Date,
  "MCFF" = Site.ID,
  Transect,
  "Station" = Station.Order..transect.,
  Easting,
  Northing,
  "Embz-1" = EmBz.residues..Rep.1...ng.kg.,
  "Embz-2" = EmBz.residues..Rep.2..ng.kg.,
  "Embz-3" = EmBz.residues..Rep.3..ng.kg.
  )

# Pivot the data into structure require for calculations
test_data <- tidyr::pivot_longer(test_data, 
                                 cols = c("Embz-1", "Embz-2", "Embz-3"), 
                                 names_to = "Station_id", values_to = "IQI")
```


## Calculate

Run data through calculations.

```{r data}
# Create a ratio otherwise Pass/Fail is wrong way around...
test_data$IQI <- 768 / test_data$IQI
output <- kraken::kraken(test_data, good_moderate = 1)
```

## Map

```{r data}

map <- output$object[output$question == "map"]
map

```

## Including Plots

Need to create a plot of the regression line based on the optimal model fitted...
Bit complicated...find which model has been used for each transect

```{r}
model <- output$object[output$question == "model_info"]
model
```


```{r plots}
# pivot output
# need unique test id!!!
# data <- output %>% dplyr::filter(question %in% c("Distance", "IQI", "MCFF_Transect"))
# data <- data %>% filter(response == "BELL1 - 1") 
# data$results_id <- sort(rep(1:7,3))
# data <- pivot_wider(data, names_from = question, values_from = response)
# 
# 
# 
# drm(IQI~Distance, Transect, data=, fct=MM.3())
# drc::MM.3()


```


