---
title: "Residue Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Residue Example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(kraken)
library(dplyr)
library(tidyr)
library(ggplot2)
library(drc)
library(ggstar)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## Data

Export data from fish farm database as .csv file. Save locally and use the 'Import Dataset' tool in the Environment pane to import data or use `read.csv()` function and paste in file path - but replace  '\' with '/' in the path.

```{r data}
# data <- read.csv("C:/Users/Tim.Foster/OneDrive - Scottish Environment Protection Agency/DNA Data/Readiness Data/ellipse-area/5279-residue.csv")

data <- read.csv(system.file("extdat", "test-data/residue-test-data.csv",
  package = "kraken"
), check.names = TRUE)
data <- dplyr::filter(data , `Site.ID` == "BELL1")
```


Prepare data for use in kraken function

```{r prepare-data}

# Select only the columns needed for calculations
data <- dplyr::select(data,
  EQS..ng.kg.,
  "Survey_date" = Survey.Date,
  "MCFF" = Site.ID,
  Transect,
  "Station" = Station.Order..transect.,
  Easting,
  Northing,
  "Embz-1" = EmBz.residues..Rep.1...ng.kg.,
  "Embz-2" = EmBz.residues..Rep.2..ng.kg.,
  "Embz-3" = EmBz.residues..Rep.3..ng.kg.
)

# Pivot the data into structure require for calculations
data <- tidyr::pivot_longer(
  data,
  cols = c("Embz-1",
           "Embz-2",
           "Embz-3"),
  names_to = "Station_id", values_to = "IQI"
)

data$IQI <- as.numeric(data$IQI)
pass_fail <- unique(na.omit(data$EQS..ng.kg.))
```


## Standard Used

```{r}
pass_fail
```


## Calculate

Run data through calculations.

```{r run-kraken, include=FALSE}
output <- kraken::kraken(data = data,
                         pass_fail = pass_fail,
                         method = "residue"
)
```

## Map

```{r map, fig.width=5, fig.height=5}
map <- output$object[output$question == "map"]
map[[1]]
```


## Breach distances

```{r}
knitr::kable(output$object[output$question == "Distance to Good (m)"])

```

### Models

Display which model or reduced analysis options have been used for each transect. 

```{r model}
model <- output$object[output$question == "model_info"][[1]]
# model <- dplyr::select(model, -MCFF, -Transect)
knitr::kable( dplyr::select(
  model,
  -MCFF,
  -Transect, 
  -reducedSamplingD2G,
  -convergedPercent,
  -dontAchieveGoodPercent ))
```


### Warnings

Display Warnings or return NA if no warnings returned. 

```{r warnings}
warnings <- output$response[grepl( "_warning", output$question)]
knitr::kable(warnings)
```


## Plots

Display plots for each transect.

```{r}
kraken:::create_plot(output, method = "residue", pass_fail = pass_fail)
```


```{r, eval=FALSE}

round(as.numeric(output$response[output$question == "area_95_confidence"],2))


```


