---
title: "Residue Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Residue Example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(kraken)
library(dplyr)
library(tidyr)
library(ggplot2)
library(drc)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning =  FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## Data

Export data from fishfarm database as .csv file. Save locally and use the 'Import Dataset' tool in the Environmment pane to import data or use `read.csv()` funtion and paste in file path - but replace  '\' with '/' in the path.

```{r data}
test_data <- read.csv(system.file("extdat/test-data/", "residue-test-data.csv", package = "kraken"))

# Filter data for my particular farm/date of interest
test_data <- dplyr::filter(test_data, Site.ID == "BELL1")

# Select only the columns needed for calculations
test_data <- dplyr::select(test_data,
  "Survey_date" = Survey.Date,
  "MCFF" = Site.ID,
  Transect,
  "Station" = Station.Order..transect.,
  Easting,
  Northing,
  "Embz-1" = EmBz.residues..Rep.1...ng.kg.,
  "Embz-2" = EmBz.residues..Rep.2..ng.kg.,
  "Embz-3" = EmBz.residues..Rep.3..ng.kg.
  )

# Pivot the data into structure require for calculations
test_data <- tidyr::pivot_longer(test_data, 
                                 cols = c("Embz-1", "Embz-2", "Embz-3"), 
                                 names_to = "Station_id", values_to = "IQI")
```


## Calculate

Run data through calculations.

```{r run-kraken}

test_data$IQI <- as.numeric(test_data$IQI)

output <- kraken::kraken(test_data,
                         good_moderate = 768, 
                         method = "residue", 
                         loess = TRUE, niter = 10)


```

## Map

```{r map}

map <- output$object[output$question == "map"]
map

```

## Including Plots

Need to create a plot of the regression line based on the optimal model fitted...
Bit complicated...find which model has been used for each transect

```{r model}

model <- output$object[output$question == "model_info"]
model
```

Model: 'Regression model fit not of sufficient quality to use' - not sure why?
Is the model struggling to fit? Wasn't a problem with earlier test data?

```{r plots}
# pivot output
data <- output %>%  dplyr::filter(grepl("BELL11", location_id))
data <- data %>% dplyr::filter(question %in% c("Distance", "IQI", "MCFF_Transect"))


# data$results_id <- sort(rep(1:7,3))
# 
# data <- distinct(data)
# data$result_id <- 1:63
# data <- pivot_wider(data, names_from = question, values_from = response)
# data <- data %>% filter(MCFF_Transect == "BELL1 - 1")
# data$IQI <- as.numeric(data$IQI)
# data$Distance <- as.numeric(data$Distance)
# 
# 
# # new data with predictions
# ggplot(aes(Distance,IQI),data = data) + 
#   geom_smooth(method=drm, method.args = list(fct = MM.3()), se = FALSE) +
#   ylab("Emmamectin PPM") +
#   ggplot2::ggtitle(paste0("Transect: ", unique(data$MCFF_Transect)))
# 
# qplot(Distance,IQI,data = data) + 
#   geom_smooth(method=drm, method.args = list(fct = MM.3()), se = FALSE) +
#   ylab("Emmamectin PPM") +
#   ggplot2::ggtitle(paste0("Transect: ", unique(data$MCFF_Transect)))
# 
# 
# drm(IQI ~ Distance,
#       data = data,
#       fct = MM.3(),
#       type = "continuous",
#       control = drmc(
#         noMessage = TRUE,
#         warnVal = -1,
#         trace = FALSE,
#         otrace = FALSE
#       )
#     )


```


