---
title: "Residue Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Residue Example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(kraken)
library(dplyr)
library(tidyr)
library(ggplot2)
library(drc)
library(ggstar)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## Data

Export data from fish farm database as .csv file. Save locally and use the 'Import Dataset' tool in the Environment pane to import data or use `read.csv()` function and paste in file path - but replace  '\' with '/' in the path.

```{r data}

# data <- read.csv("C:/Users/Tim.Foster/OneDrive - Scottish Environment Protection Agency/DNA Data/Readiness Data/ellipse-area/survey-5326-demo.csv")

data <- read.csv(system.file("extdat", "test-data/residue-test-data.csv",
  package = "kraken"
), check.names = TRUE)


data <- dplyr::filter(data , `Site.ID` == "BELL1")
# Select only the columns needed for calculations
data <- dplyr::select(data,
  EQS..ng.kg.,
  "Survey_date" = Survey.Date,
  "MCFF" = Site.ID,
  Transect,
  "Station" = Station.Order..transect.,
  Easting,
  Northing,
  "Embz-1" = EmBz.residues..Rep.1...ng.kg.,
  "Embz-2" = EmBz.residues..Rep.2..ng.kg.,
  "Embz-3" = EmBz.residues..Rep.3..ng.kg.
)

# Pivot the data into structure require for calculations
data <- tidyr::pivot_longer(
  data,
  cols = c("Embz-1",
           "Embz-2",
           "Embz-3"),
  names_to = "Station_id", values_to = "IQI"
)

data$IQI <- as.numeric(data$IQI)
pass_fail <- unique(na.omit(data$EQS..ng.kg.))
```


## Calculate

Run data through calculations.

```{r run-kraken, include=FALSE}
output <- kraken::kraken(data,
  pass_fail = pass_fail,
  method = "residue",
  ellipse_representative = TRUE
)
```

## Map

```{r map, fig.width=5, fig.height=5}
map <- output$object[output$question == "map"]
map[[1]]
```

### Models

Display which model or reduced analysis options have been used for each transect. 

```{r model}
model <- output$object[output$question == "model_info"][[1]]
# model <- dplyr::select(model, -MCFF, -Transect)
knitr::kable( dplyr::select(model, -MCFF, -Transect))
```


### Warnings

Display Warnings or return NA if no warnings returned. 

```{r warnings}
warnings <- output$response[grepl( "_warning", output$question)]
knitr::kable(warnings)
```


## Including Plots


Need to create a plot of the regression line based on the optimal model fitted...
Bit complicated...find which model has been used for each transect

Not always three reps per station. Needs to be flexible. Also may use average
value for station if two consecutive point override used.

```{r plots, eval=TRUE, fig.height=5, fig.width=5}


# pivot output
# plots_data <- output %>% dplyr::filter(grepl("FFMC27", location_id))
plots_data <- output %>% 
  dplyr::filter(question %in% c("Distance", "IQI", "MCFF_Transect"))
plots_data <- distinct(plots_data)

# plots_data <- pivot_wider(plots_data, names_from = question,
#                         values_from = response)
# plots_data$IQI <- as.numeric(plots_data$IQI)
# plots_data$Distance <- as.numeric(plots_data$Distance)


plots_data <- purrr::map_df(
  split(plots_data, plots_data$sample_id), function(sample) {
  distance <- filter(sample, question == "Distance")
  MCFF <- filter(sample, question == "MCFF_Transect")
  if(length(sample$response[sample$question == "IQI"]) == 3) { 
  sample <- bind_rows(sample, distance, distance, MCFF, MCFF)
  sample <- arrange(sample, question)
  sample$ID <- rep(1:3,3 )
  }
  if(length(sample$response[sample$question == "IQI"]) == 2) { 
  sample <- bind_rows(sample, distance, MCFF)
  sample <- arrange(sample, question)
  sample$ID <- rep(1:2,3 )
  }

  sample <- pivot_wider(sample, names_from = question, 
                          values_from = response)
sample$IQI <- as.numeric(sample$IQI)
sample$Distance <- as.numeric(sample$Distance)
  
  return(sample)
})

hex_df <- bind_rows(output$object[output$question == "hex_df"])
hex_df$Distance <- as.numeric(hex_df$Distance)
hex_df$IQI <- as.numeric(hex_df$IQI)
hex_df$Transect <- as.numeric(hex_df$Transect)
hex_df$Counts <- as.numeric(hex_df$Counts)
hex_df$shape <- NA
hex_df$size <- NA
hex_df$colour <- NA
hex_df$shape[hex_df$Source == "Prob. model"] <- "hexagon"
hex_df$shape[hex_df$Source == "Survey data"] <- "circle"
hex_df$size[hex_df$Source == "Prob. model"] <- 3
hex_df$size[hex_df$Source == "Survey data"] <- 1


breach_ensemble <- bind_rows(output$object[output$question == "breachPositionEnsemble"])
breach_ensemble <- breach_ensemble %>%
  dplyr::select(Transect, `breachDistance_95thPercentile`) %>% 
  distinct()



p <- list()
for(i in 1:nrow(model)) {
  model_plot <- model[model$Transect == i, ]
  plot_data <- plots_data[grepl(paste0("- ",i), plots_data$MCFF_Transect), ]
  model_type <- paste0(trimws(substr(model_plot$bestModel,1,4)), "()")
  message(model_type)
  transect_hex <- hex_df[hex_df$Transect == i, ]

  if(model_type %in% c("Insu()","Regr()")) {
  p[[i]] <- ggplot(aes(Distance, IQI), data = plot_data) +
  geom_point() +
  ylab("Emmamectin PPM") +
  ggplot2::ggtitle(paste0("Site: ", unique(plot_data$project_id)),
                       subtitle = paste0(unique(plot_data$MCFF_Transect),
                                         " Model fit not of sufficient quality to use")) +
  geom_hline(yintercept = pass_fail, colour = "green", linetype = 2) 
    } 
  if(!model_type %in% c("Insu()","Regr()")){
  p[[i]] <- ggplot(aes(Distance, IQI), data = plot_data) +
  geom_point() +
  geom_smooth(method = drm,
              method.args = list(fct = eval(parse(text=model_type))),
              se = FALSE) +
  ylab("Emmamectin PPM") +
  ggtitle(paste0("Site: ", unique(plot_data$project_id)), 
          subtitle = unique(plot_data$MCFF_Transect)) +
  geom_hline(yintercept = pass_fail, colour = "green", linetype = 2) 

  } 
}


for(i in 1:nrow(model)) {
  model_plot <- model[model$Transect == i, ]
  plot_data <- plots_data[grepl(paste0("- ",i), plots_data$MCFF_Transect), ]
  model_type <- paste0(trimws(substr(model_plot$bestModel,1,4)), "()")
  message(model_type)
  transect_hex <- hex_df[hex_df$Transect == i, ]
    breach <- breach_ensemble[breach_ensemble$Transect == i, ]
  if(!model_type %in% c("Insu()","Regr()")){
  p <- ggplot(aes(
    Distance,
  IQI, 
  colour = Counts, fill = Counts),
  data = transect_hex) +
  geom_star(
  starshape = transect_hex$shape,  size = transect_hex$size) +
  ylab("Emmamectin PPM") +
  ggtitle(paste0("Site: ", unique(plot_data$project_id)), 
          subtitle = unique(plot_data$MCFF_Transect)) +
  geom_hline(yintercept = pass_fail, colour = "green", linewidth = 1, linetype = 2) +
  geom_vline(xintercept = breach$breachDistance_95thPercentile,
            colour = "black", 
            linetype = 2,
            linewidth = 1) +
   scale_colour_continuous(palette = c("#FEE0D2", "#FC9272", "#DE2D26")) +
  scale_fill_continuous(palette = c("#FEE0D2", "#FC9272", "#DE2D26"))
  }
  print(p)
}


```


```{r, eval=FALSE}

output$response[output$question == "area_95_confidence"]

(100/ 196238 )  * 327687.555651631

(100/ 177068 )  * 108298

```


